Stellar Bars in Isolated Gas-Rich Spiral Galaxies Do Not Slow Down

### 2023-04-20 paper/ms.tex
Add non-lenticular slow rotators

@@

We found that below a certain gas fraction, bars should still be able to slow
down. Therefore, we expect barred spiral galaxies which have been gas-poor for
extended periods of time to be rotating very slowly. We therefore predict that
observations which target such galaxies (e.g., lenticular barred galaxies
\citep{2009ARAA..47..159B}) would find slowly rotating bars.\footnote{This does
not mean that we predict \textit{all} gas-poor galaxies should be slowly
rotating. Indeed, they would need to be gas-deficient for several $\textrm{Gyr}$
before they would be classified as slow rotators.} There does exist one example
of a galaxy which is known to be a slow rotator -- the low surface brightness
galaxy UGC 628 \citep{2009AA...499L..25C}. This galaxy has been studied in
detail by \citet{2016MNRAS.463.1751C}, who note that it indeed has a low gas
fraction for galaxies of its type. We predict a general trend that bars in
gas-rich spiral galaxies should rotate quickly while some bars in gas-poor
spiral galaxies should rotate slowly.

>>>>

{\bf There are further examples of gas-rich galaxies hosting slow bars. For
example, UGC~628 \citep[$\Rot\sim2$;][]{2009AA...499L..25C} and NGC~2915
\citep[$\Rot>1.7$;][]{1999AJ....118.2158B}. UGC~628
has been studied in detail by \citet{2016MNRAS.463.1751C}, who note that it
indeed has a low gas fraction for galaxies of its type. NGC~2915 has a gas
fraction of $0.7$ \citep{2010ApJ...715..656W}, which would seem to be in
conflict with our prediction that only a $5\%$ gas fraction is necessary to
arrest the halo slowdown process. However, NGC~2915 has significantly different
structural properties than the Milky Way-like model we considered in this work.
In particular, it has a signficantly lower mass ($\sim10^9\Msun$ compared to
$4.8\times10^{10}\Msun$ in our model). Further work is necessary to see how the
gas fraction cutoff varies with galactic properties.}

@@

We found that below a certain gas fraction, bars should still be able to slow
down. Therefore, we expect barred spiral galaxies which have been gas-poor for
extended periods of time to be rotating very slowly. We therefore predict that
observations which target such galaxies (e.g., lenticular barred galaxies
\citep{2009ARAA..47..159B}) would find slowly rotating bars.\footnote{This does
not mean that we predict \textit{all} gas-poor galaxies should be slowly
rotating. Indeed, they would need to be gas-deficient for several $\textrm{Gyr}$
before they would be classified as slow rotators.} {\bf There does exist
examples of galaxies known to be slow rotators -- the low surface brightness
galaxy UGC~628 \citep{2009AA...499L..25C}, lenticular galaxy NGC~4277
\citep{2022AA...664L..10B}, and NGC~2915 \citep{1999AJ....118.2158B}. UGC~628
has been studied in detail by \citet{2016MNRAS.463.1751C}, who note that it
indeed has a low gas fraction for galaxies of its type. NGC~2915 has a gas
fraction of $0.7$ \citep{2010ApJ...715..656W}, which would seem to be in
conflict with our prediction that only a $5\%$ gas fraction is necessary to
arrest the halo slowdown process. However, NGC~2915 has significantly different
structural properties than the Milky Way-like model we considered in this work.
In particular, it has a signficantly lower mass ($\sim10^9\Msun$ compared to
$4.8\times10^{10}\Msun$ in our model). Further work is necessary to see how the
gas fraction cutoff varies with galactic properties. TODO: shorten this} We predict a general trend
that bars in gas-rich spiral galaxies should rotate quickly while some bars in
gas-poor spiral galaxies should rotate slowly.
